---
title: "Portfolio Computational Musicology"
author: "Ellen Rosmalen"
output:
    flexdashboard::flex_dashboard:
      story: true
      theme: "journal" 
      orientation: rows 
---



```{r, include= FALSE}
library(ggplot2)
library(tidyverse)
library (flexdashboard)
library(shiny)
library(readr)
```

# Introduction {.tabset}

Row 
-----------------------

###  Text for in the introduction tab on the portfolio itself 

```{r}
valueBox('The portfolio')
```

Row 
----------------------------------

### The tracks used in this portfolio were created using StableAudio with carefully crafted prompts to achieve the desired sound. The promt used to make the two tracks was Generate an R&B track with a mix of joyful, melancholic, and romantic emotions. The music should have a warm and soulful atmosphere, featuring a smooth groove and a rhythmic beat. An expressive saxophone melody should be the centerpiece, complemented by soft electric piano chords, subtle guitar licks, and a warm bassline. The tempo should be medium to fast (around 90-110 BPM), making the track both immersive and danceable. The structure of the song should be verse-chorus-verse-chorus-bridge-chorus.’’ The seed was set at random to make two different songs with the same prompt. 

```{r}
valueBox( "The tracks ")
```

# Visualisations

Row  
----------------------------------------  
### Explanation about the visualisations/results etc  
```{r}  
# Hier komt je visualisatie voor Chart 1  
```

Row {.tabset .tabset-fade}  
----------------------------------------  
### Comparison 1   
```{r}  
# Hier komt je visualisatie voor Chart 2  
```
### Comparison 2  
```{r}  
# Hier komt je visualisatie voor Chart 3  
```




# Conclusion and Discussion

```{r}

```

 
